% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts


\begin{document}
\pagenumbering{gobble} % suppress displaying page number
% For this resume, Firstly thanks the template author .
% and then, Jiang Guo had cost nearly 1 hour to re-write it and made it more professional and clearly ,
%  Lixin Fan has mentioned many semantic errors and trival format errors ! 
% Thanks a lot .
\name{Wei Xu}

% {E-mail}{mobilephone}{homepage}
% be careful of _ in emaill address
\contactInfo{readonlyfile@hotmail.com}{(+86) 1800-451-5446}{http://memeda.github.io}
% {E-mail}{mobilephone}
% keep the last empty braces!
%\contactInfo{xxx@yuanbin.me}{(+86) 131-221-87xxx}{}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{HARBIN INSTITUTE OF TECHNOLOGY}, Harbin, China}{ Sep. 2015 -- Present}
\textit{Master student} in Computer Science (CS), expected Jul. 2017
\datedsubsection{\textbf{HARBIN INSTITUTE OF TECHNOLOGY}, Harbin, China}{ Aug. 2011 -- Jul. 2015}
\textit{B.S.} in Computer Science (CS), grads among top 10\%

\section{\faUsers\ Experience}

\datedsubsection{\textbf{Deep Learning for \\ Chinese Word Segmentation, POS Tagging, NER}}{Mar. 2016 -- Present}
\role{C++}{ Main Project }
GitHub repository : https://github.com/memeda/sequence-labeling-by-nn

The goal is to build industrial grade sequence labeling framework for NLP with high accuracy and speed.
\begin{itemize}
  \item Developed unified models that integrated neural representation learning (MLP, LSTM) with global structural inference methods (CRF).
  \item Conducted extensive experiments on benchmark datasets and obtained better score than traditional structured perceptron-based implementations in LTP (www.ltp-cloud.com).
\end{itemize}

\datedsubsection{\textbf{Text Classification on Imbalanced Datasets }}{Mar. 2015 -- Jun. 2015}
\role{Python}{Graduation Project}
GitHub repository : https://github.com/memeda/GriduationDesignCodeForTextClassification

Developed two systems respectively using boosting tree(robust) and SVM(high F1-score).
\begin{itemize}
  \item Explored a variety of models with different features and classifiers on balanced and imbalanced datasets.
  \item Improved imbalanced data classification performance by sampling, SMOTE, etc.
\end{itemize}

\datedsubsection{\textbf{Baidu Inc.} Beijing, China}{Jun. 2014 -- Sep. 2014}
\role{C/C++ , Python , shell , MapReduce}{ NLP Intern }
Deployed knowledge base extraction system in Hadoop clusters independently.
\begin{itemize}
  \item Improved shell program performance and verified kernel procedure's correctness.
  \item Deployed them in 5 Hadoop clusters simultaneously and processed data from 20K web databases.
  \item Obtained 200+ TB knowledge in one month.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: skilled in C++ , familiar with C/Python, have experiences on Shell, JS, Java.
  \item Development Experience: web(frontend), basic Linux scripts, GUI application(Qt/MFC/Java).
  \item Research Interest: text classification, sequence labeling(structure prediction), deep learning.
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textbf{National Scholarship}}{Oct. 2014}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: https://github.com/memeda
  \item Foreign Language: English - CET-6
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
